Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-08-15 ms.tex
went through section 2 for typos/fixes.

We computed brightness temperature spectra from these data as
\begin{equation}
T_{\lambda,surf} = \frac{hc}{k\lambda}\left[\ln\left(1+\frac{2\pi{hc^2}}{F_{\lambda,surf}\lambda^5}\right)\right]^{-1}
\end{equation}
where the surface flux density $F_{\lambda,surf}$ is computed as
\begin{equation}
F_{\lambda,surf} = {\pi}B_{\lambda} = F_{\lambda,obs}\left(\frac{d}{R}\right)^2 = F_{\lambda,abs}\left(\frac{10~{\rm pc}}{R}\right)^2
\end{equation}
$F_{\lambda,obs}$ and $F_{\lambda,abs}$ are the observed and absolute flux densities, $B_\lambda$ is the Planck function, $d$ the source distance and $R$ the source radius.
\textbf{We have ignored limb darkening in our calculations, which affects the surface intensity of brown dwarf surfaces \citep[e.g.][]{2011A&A...529A..75C}.
Since there are few empirical constraints on limb darkening for L-dwarfs, we assume a uniform brightness temperature surface, which gives an average brightness temperature of a non-homogeneous surface.}

@@

\begin{deluxetable*}{lccccccccc}
\tablecaption{Observations\label{tab:obsParam}}
\tablewidth{0pt}
\tablehead{
 & \multicolumn{3}{c}{Observation Epoch (UT)} \\
 \cline{2-4}
\colhead{Target} & 
\colhead{Date} & 
\colhead{Start} & 
\colhead{End} & 
\colhead{$N_{int}$} & 
\colhead{$t_{int}$} & 
\colhead{Duration} & 
\colhead{Airmass} & 
\colhead{Reference Star} & 
\colhead{FWHM \@ $H$} \\
 & &  &  & & \colhead{(s)} & \colhead{(hr)} & \colhead{Start-End} & & \colhead{(\arcsec)}}
\startdata
{\sha} & 2015-12-31 & 09:35:10 & 14:14:22 & 272 & 45 & 4.65 & 1.59-1.28 & J08354383-0819212 & 0.5 \\
{\shb} & 2016-06-25 & 07:29:31 & 14:57:58 & 352 & 60 & 7.47 & 1.42-2.15 & J18212622+1414064 & 0.5 \\
\enddata
\tablecomments{N$_{int}$ is the number of integrations and t$_{int}$ is the effective integration time for the 32 non-destructive reads up the ramp. The duration is the total time from start to end of the observations including array sampling and overheads. The FWHM is the measured full width half maximum of the spatial point spread function around 1.6$\mu$m, taken as the median value over the entire time series.}
\end{deluxetable*}

\section{Observations}\label{sec:obs}

@@

\textbf{
\subsubsection{Testing the Hemispheric Assumption}
We have previously assumed  that the there is maximum surface heterogeneity on the brown dwarf to produce the rotationally-modulated flux variations and fit for the particle size distribution.
We assumed that the clouds were confined to one East-West hemisphere between longitudes 0\degree\ and 180\degree.
We discuss here the implications of relaxing our assumption. 
Let $\alpha_{min}$ and $\alpha_{max}$ be the minimum and maximum cloud coverage.
If we assume that the clouds are optically thin, the ratio of maximum over minimum flux is
\begin{equation}
f_{R,NH} = \frac{1 - \tau \alpha_{min}}{1 - \tau \alpha_{max}},
\end{equation}
where $\tau$ is the clouds' optical depth and the $NH$ subscript denotes no hemispheric assumption.
Using Equation \ref{eq:ampFromRatio}, the amplitude is
\begin{equation}
A_{NH} = \frac{\tau \left(\alpha_{max} - \alpha_{min} \right)}{2 - \tau \left(\alpha_{max} + \alpha_{min} \right)}.
\end{equation}
In the optically thin case ($\tau \ll1$) the linear term dominates, so the amplitude, $A_{NH}$, is proportional to the optical depth $\tau$ and our assumption that $A = B \bar{Q_{avg}(r,\sigma_s)}$ is valid.
Only in the case where $\tau \gtrsim 1$ does the East-West hemispheric assumption break down. 
}
\section{Conclusions}\label{sec:conclusions}

>>>>

We computed brightness temperature spectra from these data as
\begin{equation}
T_{\lambda,surf} = \frac{hc}{k\lambda}\left[\ln\left(1+\frac{2\pi{hc^2}}{F_{\lambda,surf}\lambda^5}\right)\right]^{-1},
\end{equation}
where the surface flux density $F_{\lambda,surf}$ is computed as
\begin{equation}
F_{\lambda,surf} = {\pi}B_{\lambda} = F_{\lambda,obs}\left(\frac{d}{R}\right)^2 = F_{\lambda,abs}\left(\frac{10~{\rm pc}}{R}\right)^2.
\end{equation}
$F_{\lambda,obs}$ and $F_{\lambda,abs}$ are the observed and absolute flux densities, $B_\lambda$ is the Planck function, $d$ \textbf{is} the source distance and $R$ \textbf{is} the source radius.
\textbf{We have ignored limb darkening in our calculations, which affects the surface intensity of brown dwarf surfaces \citep[e.g.][]{2011A&A...529A..75C}.
Since there are few empirical constraints on limb darkening for L-dwarfs, we assume a uniform brightness temperature surface, which gives an average brightness temperature of a non-homogeneous surface.}

@@

\section{Observations}\label{sec:obs}
\begin{deluxetable*}{lccccccccc}
\tablecaption{Observations\label{tab:obsParam}}
\tablewidth{0pt}
\tablehead{
 & \multicolumn{3}{c}{Observation Epoch (UT)} \\
 \cline{2-4}
\colhead{Target} & 
\colhead{Date} & 
\colhead{Start} & 
\colhead{End} & 
\colhead{$N_{int}$} & 
\colhead{$t_{int}$} & 
\colhead{Duration} & 
\colhead{Airmass} & 
\colhead{Reference Star} & 
\colhead{FWHM \@ $H$} \\
 & &  &  & & \colhead{(s)} & \colhead{(hr)} & \colhead{Start-End} & & \colhead{(\arcsec)}}
\startdata
{\sha} & 2015-12-31 & 09:35:10 & 14:14:22 & 272 & 45 & 4.65 & 1.59-1.28 & J08354383-0819212 & 0.5 \\
{\shb} & 2016-06-25 & 07:29:31 & 14:57:58 & 352 & 60 & 7.47 & 1.42-2.15 & J18212622+1414064 & 0.5 \\
\enddata
\tablecomments{N$_{int}$ is the number of integrations and t$_{int}$ is the effective integration time for the 32 non-destructive reads up the ramp. The duration is the total time from start to end of the observations including array sampling and overheads. The FWHM is the measured full width half maximum of the spatial point spread function around 1.6$\mu$m, taken as the median value over the entire time series.}
\end{deluxetable*}

@@

\textbf{
\subsubsection{Exploring the Hemispheric Assumption}
We have previously assumed  that the there is maximum surface heterogeneity on the brown dwarf to produce the rotationally-modulated flux variations and fit for the particle size distribution.
We assumed that the clouds were confined to one East-West hemisphere between longitudes 0\degree\ and 180\degree.
We discuss here the implications of relaxing our assumption. 
Let $\alpha_{min}$ and $\alpha_{max}$ be the minimum and maximum cloud coverage.
If we assume that the clouds are optically thin, the ratio of maximum over minimum flux is
\begin{equation}
f_{R,NH} = \frac{1 - \tau \alpha_{min}}{1 - \tau \alpha_{max}},
\end{equation}
where $\tau$ is the clouds' optical depth and the $NH$ subscript denotes no hemispheric assumption.
Using Equation \ref{eq:ampFromRatio}, the amplitude is
\begin{equation}
A_{NH} = \frac{\tau \left(\alpha_{max} - \alpha_{min} \right)}{2 - \tau \left(\alpha_{max} + \alpha_{min} \right)}.
\end{equation}
In the optically thin case ($\tau \ll1$) the linear term dominates, so the amplitude, $A_{NH}$, is proportional to the optical depth $\tau$ and our assumption that $A = B \bar{Q_{avg}(r,\sigma_s)}$ is valid.
Only in the case where $\tau \gtrsim 1$ does the East-West hemispheric assumption break down. 
}
\section{Conclusions}\label{sec:conclusions}
